GVN-Hoist: Hoisting Computations from Branches

### 2016-08-09 hoist.tex
optimistic

\subsection{Checking for legality}
Finding a hoisting point i.e., a common dominator of the set of instructions. If
such a dominator is found then checking if all the use-operands of the set of
instructions are available or not. In some cases when the operands are not
available, it is possible to reinstantiate (remateralize) the use-operands, thus
passing the legality check. Checking that the side-effects of the computations
does not intersect with any side-effects between the instructions to be hoisted
and their hoisting point. For memory operations like loads, stores, calls etc.,
it is also required to check that all the paths from the hoisting point to the
end of the function should execute the exact instruction, in order to guarantee
correctness. Moreover, hoisting of memory operations is tricky on paths which
have indirect branch targets e.g., landing pad, case statements, goto labels
etc., because it becomes difficult to prove that all the paths from hoisting
point to the end of the function would execute the instruction. In our current
implementation we discard hoisting through such paths.

@@

\subsection{Checking for profitability}
Establishing a set of cost models tune for performance. Like decreasing code
size, minimizing spills etc.

@@

\subsection{Hoisting bottom up with optimistic approach}
\label{subsec:optimistic}
In this approach, the goal is to maximise the total number of hoistings in the
entire function.  This algorithm is very useful when optimizing for code-size.
In order to do that, we collect the GVN of all the instructions in the
function. After that we iterate on the list of instructions having identical
GVNs. After that we find the common dominator dominating all the identical
computations and try to hoist the instruction in that basic block, if
feasible. Many times it is not possible to hoist all the instructions to one
common dominator, due to legality/profitability constraints. In those cases, the
algorithmn would partion the list of computations and partially hoist a set of
computations to their common dominator. For more details see
Section-\ref{subsec:partition}.

@@

In order to hoist a subset of identical instructions, we partition the
list of all candidates in a way to maximise the total number of
hoistings.  By sorting the list of all the candidates in the
increasing order of their DFS-in numbers, we make sure that candidates
closer in the list have their common dominator nearby.

In our current implementation we partition the list at the point where the
legality/profitability checks fail.

>>>>

\subsection{Checking for legality}
\label{subsec:legality}
Finding a hoisting point i.e., a common dominator of the set of instructions. If
such a dominator is found then checking if all the use-operands of the set of
instructions are available or not. In some cases when the operands are not
available, it is possible to reinstantiate (remateralize) the use-operands, thus
passing the legality check. Checking that the side-effects of the computations
does not intersect with any side-effects between the instructions to be hoisted
and their hoisting point. For memory operations like loads, stores, calls etc.,
it is also required to check that all the paths from the hoisting point to the
end of the function should execute the exact instruction, in order to guarantee
correctness. Moreover, hoisting of memory operations is tricky on paths which
have indirect branch targets e.g., landing pad, case statements, goto labels
etc., because it becomes difficult to prove that all the paths from hoisting
point to the end of the function would execute the instruction. In our current
implementation we discard hoisting through such paths.

@@

\subsection{Checking for profitability}
\label{subsec:profitability}
Establishing a set of cost models tune for performance. Like decreasing code
size, minimizing spills etc.

@@

\subsection{Hoisting bottom up with optimistic approach}
\label{subsec:optimistic}
In this approach, the goal is to maximise the total number of hoistings in the
entire function.  This algorithm is very useful when optimizing for code-size.
In order to do that, we collect the GVN of all the instructions in the function
and iterate on the list of instructions having identical GVNs. After that we
find the common dominator dominating all the identical computations and perform
legality checks (Section-\ref{subsec:legality}). Many times it is not possible
to hoist all the instructions to one common dominator, due to legality
constraints e.g., intersecting side-effects or, profitability constraints e.g.,
hoisting point too far. In those cases, the algorithmn would partition the list
of computations and partially hoist a set of computations to their common
dominator. For more details see Section-\ref{subsec:partition}.

In order to hoist a subset of identical instructions, we partition the list of
all candidates in a way to maximise the total number of hoistings.  By sorting
the list of all the candidates in the increasing order of their DFS-in numbers,
we make sure that candidates closer in the list have their common dominator
nearby in cases when there are no fully redundant instructions.

In case of fully redundant computations the nearby elements may not be 'closer'
than the separated ones. TODO: Explain.

In our current implementation we partition the list at the point where the
legality checks fail.

@@
